Greenhouse gas emissions model

### 2021-09-06 210617_GHG_model.Rmd
Draft for discussion with Todd and Andy

```{r monte_carlo_simulation}
GHG_simulation <- mcSimulation(
  estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
  model_function = ghg_emissions,
  numberOfModelRuns = 1e2, #100 for now
  functionSyntax = "plainNames"
)
```

@@

## Milk_yield (x-axis) effect on on farm GHG emissions (y-axis)

>>>>

```{r monte_carlo_simulation}
GHG_simulation <- mcSimulation(
  estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
  model_function = ghg_emissions,
  numberOfModelRuns = 1e4, # 10,000 runs
  functionSyntax = "plainNames"
)
```

@@

## Milk_yield (x-axis) effect on on-farm GHG emissions (y-axis)
